A Switching Planner for Combined Task and Observation Planning

### 2011-01-19 code/subarchitectures/planner.sa/trunk/src/latex/IJCAI/ijcai11.tex
Moritz, I put your diagram back into the system

\typeout{IJCAI-11 Instructions for Authors}

@@

\usepackage{subfig}
%% \usepackage{tikz}
%% \usetikzlibrary{shapes}
%% \usetikzlibrary{positioning}

@@

%% \begin{figure}[h!]
%%   \centering
%%   \tikzstyle{tree} = [sibling distance=4.5mm]
%%   \tikzstyle{toplevel} = [grow'=right, sibling distance=22mm]
%%   \tikzstyle{seclevel} = [sibling distance=9mm]
%%   \tikzstyle{pnode} = [diamond, draw=black, minimum size=2.5mm]
%%   \tikzstyle{cnode} = [circle, draw=black, minimum size=3mm]
%%   \tikzstyle{assumption} = [solid, very thick, draw=black]
%%   \tikzstyle{selected} = [solid, draw=black]
%%   \tikzstyle{unused} = [densely dashed, draw=black!40]
%%   \subfloat[The initial belief-state with the assumptions made by the continual
%%     planner in bold.]{
%%       \label{fig:abstraction-a}
%%       \begin{tikzpicture}[
%%     level 3/.style={tree}]
%%     \node[pnode, assumption] (cat) at (1,1) {} [toplevel]
%%       child[seclevel] {node[cnode, assumption] (office) {}
%%         child {node [pnode, assumption] (box) {}
%%           child {node [cnode] (boxp1) {}}
%%           child {node [cnode, assumption] (boxp2) {}}
%%         }
%%         child {node [pnode] (cup) {} 
%%           child {node [cnode] (cupp1) {}}
%%           child {node [cnode] (cupp2) {}}
%%         }
%%       }
%%       child {node[cnode] (kitchen) {}
%%         child {node [pnode] (box2) {} 
%%           child {node [cnode] (box2p1) {}}
%%           child {node [cnode] (box2p2) {}}
%%         }
%%       };
%%    \tiny
%%    \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
%%    \node[above=0 of cat] {$\pp{(category room1)}$};
%%    \node[below=0 of kitchen] {$\pp{kitchen}$};
%%    \node[below=0 of office] {$\pp{office}$};
%%    \node[below=0 of box] {$\pp{(is-in box)}$};
%%    \node[below=0 of box2] {$\pp{(is-in box)}$};
%%    \node[below=0 of cup] {$\pp{(is-in cup)}$};
%%    \node[right=0 of boxp1] {$\pp{place1}$};
%%    \node[right=0 of boxp2] {$\pp{place2}$};
%%    \node[right=0 of box2p1] {$\pp{place1}$};
%%    \node[right=0 of box2p2] {$\pp{place2}$};
%%    \node[right=0 of cupp1] {$\pp{place1}$};
%%    \node[right=0 of cupp2] {$\pp{place2}$};
%%     % \node[node] (kitchen) right of (cat) {};
%%   \end{tikzpicture}}
%% \qquad
%%   \subfloat[Removing facts that are not part of an assumption.]{
%%     \label{fig:abstraction-b}
%%     \begin{tikzpicture}[
%%     level 3/.style={tree}]
%%     \node[pnode, assumption] (cat) at (1,1) {} [toplevel, unused]
%%       child[seclevel] {node[cnode, assumption] (office) {}
%%         child {node [pnode, assumption] (box) {}
%%           child {node [cnode, unused] (boxp1) {}}
%%           child {node [cnode, assumption] (boxp2) {}}
%%         }
%%         child {node [pnode, unused] (cup) {} 
%%           child {node [cnode, unused] (cupp1) {}}
%%           child {node [cnode, unused] (cupp2) {}}
%%         }
%%       }
%%       child {node[cnode, selected] (kitchen) {}
%%         child {node [pnode, selected] (box2) {} 
%%           child {node [cnode, unused] (box2p1) {}}
%%           child {node [cnode, selected] (box2p2) {}}
%%         }
%%       };
%%    \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
%%    \draw[selected] (cat) -- (kitchen) -- (box2) -- (box2p2);
%%    \tiny
%%    \node[above=0 of cat] {$\pp{(category room1)}$};
%%    \node[below=0 of office] {$\pp{office}$};
%%    \node[below=0 of box] {$\pp{(is-in box)}$};
%%    \node[below=0 of box2] {$\pp{(is-in box)}$};
%%    \node[right=0 of boxp2] {$\pp{place2}$};
%%    \node[right=0 of box2p2] {$\pp{place2}$};
%%     % \node[node] (kitchen) right of (cat) {};
%%   \end{tikzpicture}}
%% \vspace{2mm}
%%   \subfloat[Refinement, by adding relevant facts until the $\bstate_0$ size limit is reached.]{
%%     \label{fig:abstraction-c}
%%     \begin{tikzpicture}[
%%     level 3/.style={tree}]
%%     \node[pnode, assumption] (cat) at (1,1) {} [toplevel, unused]
%%       child[seclevel] {node[cnode, assumption] (office) {}
%%         child {node [pnode, assumption] (box) {}
%%           child {node [cnode, selected] (boxp1) {}}
%%           child {node [cnode, assumption] (boxp2) {}}
%%         }
%%         child {node [pnode, unused] (cup) {} 
%%           child {node [cnode, unused] (cupp1) {}}
%%           child {node [cnode, unused] (cupp2) {}}
%%         }
%%       }
%%       child {node[cnode, selected] (kitchen) {}
%%         child {node [pnode, selected] (box2) {} 
%%           child {node [cnode, selected] (box2p1) {}}
%%           child {node [cnode, selected] (box2p2) {}}
%%         }
%%       };
%%    \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
%%    \draw[selected] (box) -- (boxp1);
%%    \draw[selected] (cat) -- (kitchen) -- (box2) -- (box2p2);
%%    \draw[selected] (box2) -- (box2p1);
%%    \tiny
%%    \node[above=0 of cat] {$\pp{(category room1)}$};
%%    \node[below=0 of office] {$\pp{office}$};
%%    \node[below=0 of box] {$\pp{(is-in box)}$};
%%    \node[below=0 of box2] {$\pp{(is-in box)}$};
%%    \node[right=0 of boxp1] {$\pp{place1}$};
%%    \node[right=0 of boxp2] {$\pp{place2}$};
%%    \node[right=0 of box2p1] {$\pp{place1}$};
%%    \node[right=0 of box2p2] {$\pp{place2}$};
%%     % \node[node] (kitchen) right of (cat) {};
%%   \end{tikzpicture}}

%%   \caption{Generating the abstract belief space.}
%% \label{fig:abstraction}
%% \end{figure}

>>>>

\typeout{IJCAI Switching Planner Submission}

@@

\usepackage{subfig}
\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{positioning}

@@

\begin{figure}[h!]
  \centering
  \tikzstyle{tree} = [sibling distance=4.5mm]
  \tikzstyle{toplevel} = [grow'=right, sibling distance=22mm]
  \tikzstyle{seclevel} = [sibling distance=9mm]
  \tikzstyle{pnode} = [diamond, draw=black, minimum size=2.5mm]
  \tikzstyle{cnode} = [circle, draw=black, minimum size=3mm]
  \tikzstyle{assumption} = [solid, very thick, draw=black]
  \tikzstyle{selected} = [solid, draw=black]
  \tikzstyle{unused} = [densely dashed, draw=black!40]
  \subfloat[The initial belief-state with the assumptions made by the continual
    planner in bold.]{
      \label{fig:abstraction-a}
      \begin{tikzpicture}[
    level 3/.style={tree}]
    \node[pnode, assumption] (cat) at (1,1) {} [toplevel]
      child[seclevel] {node[cnode, assumption] (office) {}
        child {node [pnode, assumption] (box) {}
          child {node [cnode] (boxp1) {}}
          child {node [cnode, assumption] (boxp2) {}}
        }
        child {node [pnode] (cup) {} 
          child {node [cnode] (cupp1) {}}
          child {node [cnode] (cupp2) {}}
        }
      }
      child {node[cnode] (kitchen) {}
        child {node [pnode] (box2) {} 
          child {node [cnode] (box2p1) {}}
          child {node [cnode] (box2p2) {}}
        }
      };
   \tiny
   \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
   \node[above=0 of cat] {$\pp{(category room1)}$};
   \node[below=0 of kitchen] {$\pp{kitchen}$};
   \node[below=0 of office] {$\pp{office}$};
   \node[below=0 of box] {$\pp{(is-in box)}$};
   \node[below=0 of box2] {$\pp{(is-in box)}$};
   \node[below=0 of cup] {$\pp{(is-in cup)}$};
   \node[right=0 of boxp1] {$\pp{place1}$};
   \node[right=0 of boxp2] {$\pp{place2}$};
   \node[right=0 of box2p1] {$\pp{place1}$};
   \node[right=0 of box2p2] {$\pp{place2}$};
   \node[right=0 of cupp1] {$\pp{place1}$};
   \node[right=0 of cupp2] {$\pp{place2}$};
    % \node[node] (kitchen) right of (cat) {};
  \end{tikzpicture}}
\qquad
  \subfloat[Removing facts that are not part of an assumption.]{
    \label{fig:abstraction-b}
    \begin{tikzpicture}[
    level 3/.style={tree}]
    \node[pnode, assumption] (cat) at (1,1) {} [toplevel, unused]
      child[seclevel] {node[cnode, assumption] (office) {}
        child {node [pnode, assumption] (box) {}
          child {node [cnode, unused] (boxp1) {}}
          child {node [cnode, assumption] (boxp2) {}}
        }
        child {node [pnode, unused] (cup) {} 
          child {node [cnode, unused] (cupp1) {}}
          child {node [cnode, unused] (cupp2) {}}
        }
      }
      child {node[cnode, selected] (kitchen) {}
        child {node [pnode, selected] (box2) {} 
          child {node [cnode, unused] (box2p1) {}}
          child {node [cnode, selected] (box2p2) {}}
        }
      };
   \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
   \draw[selected] (cat) -- (kitchen) -- (box2) -- (box2p2);
   \tiny
   \node[above=0 of cat] {$\pp{(category room1)}$};
   \node[below=0 of office] {$\pp{office}$};
   \node[below=0 of box] {$\pp{(is-in box)}$};
   \node[below=0 of box2] {$\pp{(is-in box)}$};
   \node[right=0 of boxp2] {$\pp{place2}$};
   \node[right=0 of box2p2] {$\pp{place2}$};
    % \node[node] (kitchen) right of (cat) {};
  \end{tikzpicture}}
\vspace{2mm}
  \subfloat[Refinement, by adding relevant facts until the $\bstate_0$ size limit is reached.]{
    \label{fig:abstraction-c}
    \begin{tikzpicture}[
    level 3/.style={tree}]
    \node[pnode, assumption] (cat) at (1,1) {} [toplevel, unused]
      child[seclevel] {node[cnode, assumption] (office) {}
        child {node [pnode, assumption] (box) {}
          child {node [cnode, selected] (boxp1) {}}
          child {node [cnode, assumption] (boxp2) {}}
        }
        child {node [pnode, unused] (cup) {} 
          child {node [cnode, unused] (cupp1) {}}
          child {node [cnode, unused] (cupp2) {}}
        }
      }
      child {node[cnode, selected] (kitchen) {}
        child {node [pnode, selected] (box2) {} 
          child {node [cnode, selected] (box2p1) {}}
          child {node [cnode, selected] (box2p2) {}}
        }
      };
   \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
   \draw[selected] (box) -- (boxp1);
   \draw[selected] (cat) -- (kitchen) -- (box2) -- (box2p2);
   \draw[selected] (box2) -- (box2p1);
   \tiny
   \node[above=0 of cat] {$\pp{(category room1)}$};
   \node[below=0 of office] {$\pp{office}$};
   \node[below=0 of box] {$\pp{(is-in box)}$};
   \node[below=0 of box2] {$\pp{(is-in box)}$};
   \node[right=0 of boxp1] {$\pp{place1}$};
   \node[right=0 of boxp2] {$\pp{place2}$};
   \node[right=0 of box2p1] {$\pp{place1}$};
   \node[right=0 of box2p2] {$\pp{place2}$};
    % \node[node] (kitchen) right of (cat) {};
  \end{tikzpicture}}

  \caption{Generating the abstract belief space.}
\label{fig:abstraction}
\end{figure}
